---
title: "GreenLeaf CEA — Agribusiness Analytics Hackathon 2026"
subtitle: "Exploratory Data Analysis, Trend Analysis & Dashboard CSV Generation"
author: "Team [Your Team Name]"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    theme: flatly
    highlight: tango
    code_folding: show
---

```{r setup, include=FALSE}
setwd('/Users/lavikasingh/Documents/SFU/Hackathons/Beedie RBC 2026 Hackathon/hackathon files')
knitr::opts_chunk$set(
  echo    = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.width  = 12,
  fig.height = 6,
  fig.align  = "center"
)
```

# 0. Setup — Load Libraries and Data

```{r libraries}
library(tidyverse)    # dplyr, ggplot2, tidyr, readr, purrr
library(lubridate)    # date handling
library(scales)       # axis formatting
library(corrplot)     # correlation matrix
library(RColorBrewer) # colour palettes
```

```{r load-data}
sensor      <- read_csv("daily_sensor_readings.csv")
costs       <- read_csv("daily_input_costs.csv")
plots       <- read_csv("plots.csv")
farms       <- read_csv("farms.csv")
greenhouses <- read_csv("greenhouses.csv")
inputs      <- read_csv("input_applications.csv")
season      <- read_csv("season_summary.csv")
scouting    <- read_csv("scouting_observations.csv")
prices      <- read_csv("market_and_input_prices.csv")

# Parse dates
sensor   <- sensor   %>% mutate(date = as.Date(date))
costs    <- costs    %>% mutate(date = as.Date(date))
inputs   <- inputs   %>% mutate(date = as.Date(date))
scouting <- scouting %>% mutate(date = as.Date(date))
prices   <- prices   %>% mutate(date = as.Date(date))

# Add time fields
sensor <- sensor %>%
  mutate(
    week_num   = isoweek(date),
    year       = year(date),
    month      = month(date, label = TRUE),
    week_label = paste0("Week ", week_num)
  )

cat("Data loaded successfully\n")
cat("Sensor rows     :", nrow(sensor), "\n")
cat("Date range      :", as.character(min(sensor$date)),
    "to", as.character(max(sensor$date)), "\n")
cat("Unique plots    :", n_distinct(sensor$plot_id), "\n")
cat("Unique weeks    :", n_distinct(sensor$week_num), "\n")
```

---

# 1. Dataset Overview

```{r dataset-overview}
overview <- data.frame(
  Dataset = c("daily_sensor_readings","daily_input_costs","plots","farms",
              "greenhouses","input_applications","season_summary",
              "scouting_observations","market_and_input_prices"),
  Rows    = c(nrow(sensor), nrow(costs), nrow(plots), nrow(farms),
              nrow(greenhouses), nrow(inputs), nrow(season),
              nrow(scouting), nrow(prices)),
  Columns = c(ncol(sensor), ncol(costs), ncol(plots), ncol(farms),
              ncol(greenhouses), ncol(inputs), ncol(season),
              ncol(scouting), ncol(prices))
)
print(overview)
```

```{r missing-values}
cat("=== Missing Values in Sensor Data ===\n")
missing <- colSums(is.na(sensor))
missing <- missing[missing > 0]
print(round(missing / nrow(sensor) * 100, 1))
```

```{r crop-treatment-distribution}
cat("=== Plot Distribution by Crop and Treatment ===\n")
print(table(plots$crop, plots$treatment))
```

---

# 2. EDA — Sensor Data

## 2.1 Stress Index Distribution

```{r stress-distribution}
pct_high <- round(mean(sensor$plant_stress_index > 0.6) * 100, 1)

ggplot(sensor, aes(x = plant_stress_index)) +
  geom_histogram(bins = 50, fill = "#E05A4E", alpha = 0.8, colour = "white") +
  geom_vline(xintercept = 0.6, colour = "darkred",
             linetype = "dashed", linewidth = 1) +
  geom_vline(xintercept = 0.7, colour = "black",
             linetype = "dashed", linewidth = 1) +
  annotate("text", x = 0.63, y = 1200,
           label = "High stress (0.6)", size = 3.5, colour = "darkred") +
  annotate("text", x = 0.73, y = 1000,
           label = "Critical (0.7)", size = 3.5, colour = "black") +
  scale_x_continuous(limits = c(0, 1)) +
  labs(
    title    = "Distribution of Plant Stress Index — Full Season",
    subtitle = paste0(pct_high, "% of plot-days above 0.6 high stress threshold"),
    x = "Plant Stress Index (0 = healthy, 1 = critical)",
    y = "Number of plot-days"
  ) +
  theme_minimal(base_size = 13)
```

```{r stress-by-crop}
ggplot(sensor, aes(x = reorder(crop, plant_stress_index, median),
                   y = plant_stress_index, fill = crop)) +
  geom_boxplot(alpha = 0.8, outlier.alpha = 0.2) +
  geom_hline(yintercept = 0.6, colour = "red", linetype = "dashed") +
  scale_fill_brewer(palette = "Set2") +
  labs(
    title    = "Plant Stress Index by Crop",
    subtitle = "Red dashed line = high stress threshold (0.6)",
    x = "Crop", y = "Plant Stress Index"
  ) +
  theme_minimal(base_size = 13) +
  theme(legend.position = "none")
```

```{r stress-by-treatment}
sensor %>%
  left_join(plots %>% select(plot_id, treatment), by = "plot_id") %>%
  group_by(treatment) %>%
  summarise(avg_stress = mean(plant_stress_index), .groups = "drop") %>%
  arrange(desc(avg_stress)) %>%
  ggplot(aes(x = reorder(treatment, avg_stress),
             y = avg_stress, fill = avg_stress)) +
  geom_col(alpha = 0.9) +
  geom_hline(yintercept = 0.6, colour = "red", linetype = "dashed") +
  geom_text(aes(label = round(avg_stress, 3)), hjust = -0.2, size = 3.5) +
  scale_fill_gradient(low = "#78C96B", high = "#E05A4E") +
  coord_flip() +
  labs(
    title    = "Average Plant Stress Index by Treatment",
    subtitle = "Shade and Reduced Pest treatments show highest stress",
    x = "Treatment", y = "Average Plant Stress Index"
  ) +
  theme_minimal(base_size = 13) +
  theme(legend.position = "none")
```

## 2.2 Alert Analysis

```{r alert-overview}
cat("=== Alert Type Distribution — Full Season ===\n")
alert_counts <- sensor %>%
  filter(alert_flag == 1) %>%
  count(alert_type) %>%
  mutate(pct = round(n / sum(n) * 100, 1)) %>%
  arrange(desc(n))
print(alert_counts)
```

```{r alert-by-crop}
sensor %>%
  filter(alert_flag == 1) %>%
  count(crop, alert_type) %>%
  ggplot(aes(x = reorder(alert_type, n), y = n, fill = crop)) +
  geom_col(position = "dodge", alpha = 0.85) +
  scale_fill_brewer(palette = "Set2") +
  coord_flip() +
  labs(
    title = "Alert Count by Type and Crop — Full Season",
    x = "Alert Type", y = "Number of Alerts", fill = "Crop"
  ) +
  theme_minimal(base_size = 13)
```

```{r response-rate}
cat("=== Overall Alert Response Summary ===\n")
sensor %>%
  filter(alert_flag == 1) %>%
  summarise(
    total_alerts  = n(),
    total_actions = sum(action_taken, na.rm = TRUE),
    action_rate   = round(mean(action_taken, na.rm = TRUE), 3),
    avg_delay     = round(mean(action_delay_days, na.rm = TRUE), 3),
    same_day_pct  = round(mean(action_delay_days == 0, na.rm = TRUE) * 100, 1)
  ) %>%
  print()
```

## 2.3 Correlation Analysis

```{r correlation-matrix}
cor_vars <- sensor %>%
  select(
    plant_stress_index, pest_pressure_index, disease_risk_index,
    air_temp_c, relative_humidity_pct, vpd_kpa,
    substrate_moisture, substrate_ec, canopy_temp_c, alert_flag
  ) %>%
  drop_na()

cor_matrix <- cor(cor_vars)

corrplot(
  cor_matrix,
  method      = "color",
  type        = "upper",
  tl.cex      = 0.8,
  tl.col      = "black",
  addCoef.col = "black",
  number.cex  = 0.7,
  col         = colorRampPalette(c("#4575B4","white","#D73027"))(200),
  title       = "Correlation Matrix — Key Sensor Variables",
  mar         = c(0, 0, 2, 0)
)
```

---

# 3. Trend Analysis

## 3.1 Weekly Stress Trend

```{r weekly-stress-trend}
weekly_stress <- sensor %>%
  group_by(week_num) %>%
  summarise(
    avg_stress   = mean(plant_stress_index),
    max_stress   = max(plant_stress_index),
    alert_count  = sum(alert_flag),
    action_count = sum(action_taken, na.rm = TRUE),
    action_rate  = mean(action_taken[alert_flag == 1], na.rm = TRUE),
    .groups = "drop"
  )

ggplot(weekly_stress, aes(x = week_num)) +
  geom_ribbon(aes(ymin = avg_stress - 0.05, ymax = avg_stress + 0.05),
              fill = "#E05A4E", alpha = 0.2) +
  geom_line(aes(y = avg_stress), colour = "#E05A4E", linewidth = 1.2) +
  geom_point(aes(y = avg_stress, size = alert_count),
             colour = "#E05A4E", alpha = 0.7) +
  geom_hline(yintercept = 0.6, linetype = "dashed", colour = "darkred") +
  annotate("text", x = max(weekly_stress$week_num), y = 0.62,
           label = "High stress threshold", hjust = 1,
           size = 3, colour = "darkred") +
  scale_size_continuous(name = "Alert count", range = c(2, 8)) +
  scale_x_continuous(breaks = seq(7, 37, by = 2)) +
  labs(
    title    = "Weekly Average Plant Stress Index — Full Season",
    subtitle = "Point size = number of alerts that week",
    x = "Week Number", y = "Avg Plant Stress Index"
  ) +
  theme_minimal(base_size = 13)
```

## 3.2 Weekly Response Rate Trend

```{r weekly-response-trend}
ggplot(weekly_stress, aes(x = week_num)) +
  geom_col(aes(y = alert_count / max(alert_count)),
           fill = "#AFA9EC", alpha = 0.5) +
  geom_line(aes(y = action_rate), colour = "#0F6E56", linewidth = 1.2) +
  geom_point(aes(y = action_rate), colour = "#0F6E56", size = 2) +
  geom_hline(yintercept = 0.5, linetype = "dashed", colour = "red") +
  scale_x_continuous(breaks = seq(7, 37, by = 2)) +
  labs(
    title    = "Weekly Action Rate vs Alert Volume — Full Season",
    subtitle = "Green line = action rate | Purple bars = alert volume | Red = 50% threshold",
    x = "Week Number",
    y = "Action Rate / Normalised Alert Count"
  ) +
  theme_minimal(base_size = 13)
```

## 3.3 Delay Impact on Stress Outcomes

```{r delay-impact}
delay_analysis <- sensor %>%
  filter(action_taken == 1, !is.na(post_action_stress_delta_3d)) %>%
  mutate(
    delay_bucket = case_when(
      action_delay_days == 0 ~ "Same day (0d)",
      action_delay_days == 1 ~ "1 day later",
      action_delay_days == 2 ~ "2 days later",
      TRUE ~ "Other"
    )
  ) %>%
  filter(delay_bucket != "Other") %>%
  group_by(delay_bucket) %>%
  summarise(
    count        = n(),
    avg_delta    = mean(post_action_stress_delta_3d),
    pct_improved = mean(post_action_stress_delta_3d < 0) * 100,
    .groups = "drop"
  ) %>%
  mutate(delay_bucket = factor(delay_bucket,
    levels = c("Same day (0d)", "1 day later", "2 days later")))

cat("=== Delay Impact on Stress Outcomes ===\n")
print(delay_analysis)

ggplot(delay_analysis, aes(x = delay_bucket, y = avg_delta,
                           fill = delay_bucket)) +
  geom_col(alpha = 0.9, width = 0.6) +
  geom_text(aes(label = round(avg_delta, 3)),
            vjust = 1.5, colour = "white",
            fontface = "bold", size = 4.5) +
  geom_hline(yintercept = 0, colour = "black", linewidth = 0.8) +
  scale_fill_manual(values = c(
    "Same day (0d)" = "#0F6E56",
    "1 day later"   = "#F5A623",
    "2 days later"  = "#E05A4E"
  )) +
  labs(
    title    = "Impact of Response Speed on Stress Reduction",
    subtitle = "Same-day response is 78% more effective than a 2-day delay",
    x       = "Response Speed",
    y       = "Avg Stress Delta (3 days post-action)",
    caption = "Negative = stress improved. Green = best, Red = worst."
  ) +
  theme_minimal(base_size = 13) +
  theme(legend.position = "none")
```

## 3.4 Season ROI by Action Rate Quartile

```{r roi-by-action-rate}
week14_summary <- sensor %>%
  filter(week_num == 14) %>%
  group_by(plot_id) %>%
  summarise(
    alert_count  = sum(alert_flag),
    action_count = sum(action_taken, na.rm = TRUE),
    max_stress   = max(plant_stress_index),
    avg_stress   = mean(plant_stress_index),
    avg_delay    = mean(action_delay_days, na.rm = TRUE),
    avg_delta    = mean(post_action_stress_delta_3d, na.rm = TRUE),
    days         = n(),
    .groups = "drop"
  ) %>%
  mutate(
    alert_rate      = alert_count / days,
    action_rate     = ifelse(alert_count > 0, action_count / alert_count, 0),
    action_quartile = ntile(action_rate, 4)
  ) %>%
  left_join(season, by = "plot_id")

roi_by_quartile <- week14_summary %>%
  group_by(action_quartile) %>%
  summarise(
    avg_roi           = round(mean(season_roi, na.rm = TRUE), 3),
    avg_prec_benefit  = round(mean(precision_benefit_cad, na.rm = TRUE), 0),
    n_plots           = n(),
    .groups = "drop"
  ) %>%
  mutate(label = c("Q1 Low","Q2","Q3","Q4 High"))

cat("=== Season ROI by Action Rate Quartile ===\n")
print(roi_by_quartile)

ggplot(roi_by_quartile, aes(x = label, y = avg_roi, fill = label)) +
  geom_col(alpha = 0.85, width = 0.6) +
  geom_text(aes(label = round(avg_roi, 3)), vjust = -0.5, size = 4) +
  scale_fill_manual(values = c(
    "Q1 Low" = "#E05A4E",
    "Q2"     = "#F5A623",
    "Q3"     = "#78C96B",
    "Q4 High"= "#0F6E56"
  )) +
  labs(
    title    = "Season ROI by Alert Response Rate Quartile — Week 14",
    subtitle = "Plots responding to more alerts earned higher end-of-season ROI",
    x = "Action Rate Quartile", y = "Average Season ROI"
  ) +
  theme_minimal(base_size = 13) +
  theme(legend.position = "none")
```

## 3.5 Precision vs Routine Actions

```{r precision-vs-routine}
cat("=== Stress Outcomes: Precision vs Routine Actions ===\n")
inputs %>%
  left_join(
    sensor %>% select(date, plot_id, post_action_stress_delta_3d),
    by = c("date","plot_id")
  ) %>%
  filter(!is.na(post_action_stress_delta_3d)) %>%
  mutate(action_type = ifelse(
    is_precision_action == 1, "Precision", "Routine")) %>%
  group_by(action_type) %>%
  summarise(
    avg_delta    = round(mean(post_action_stress_delta_3d), 4),
    pct_improved = round(mean(post_action_stress_delta_3d < 0) * 100, 1),
    avg_cost     = round(mean(total_cost, na.rm = TRUE), 2),
    count        = n(),
    .groups = "drop"
  ) %>%
  print()
```

---

# 4. Financial Analysis

## 4.1 Season Profitability by Crop

```{r profitability-overview}
cat("=== Season Financial Summary by Crop ===\n")
season %>%
  left_join(plots %>% select(plot_id, crop, treatment), by = "plot_id") %>%
  group_by(crop) %>%
  summarise(
    avg_yield        = round(mean(season_yield_kg_m2), 2),
    avg_marketable   = round(mean(marketable_ratio) * 100, 1),
    avg_revenue      = round(mean(season_revenue_cad), 0),
    avg_cost         = round(mean(total_cost_cad), 0),
    avg_profit       = round(mean(season_profit_cad), 0),
    avg_roi          = round(mean(season_roi), 3),
    avg_prec_benefit = round(mean(precision_benefit_cad), 0),
    .groups = "drop"
  ) %>%
  print()
```

```{r roi-by-treatment}
season %>%
  left_join(plots %>% select(plot_id, treatment), by = "plot_id") %>%
  group_by(treatment) %>%
  summarise(avg_roi = mean(season_roi), .groups = "drop") %>%
  arrange(desc(avg_roi)) %>%
  ggplot(aes(x = reorder(treatment, avg_roi),
             y = avg_roi, fill = avg_roi)) +
  geom_col(alpha = 0.85) +
  geom_text(aes(label = round(avg_roi, 3)), hjust = -0.2, size = 3.5) +
  scale_fill_gradient(low = "#E05A4E", high = "#0F6E56") +
  coord_flip() +
  labs(
    title = "Average Season ROI by Treatment",
    x = "Treatment", y = "Average Season ROI"
  ) +
  theme_minimal(base_size = 13) +
  theme(legend.position = "none")
```

## 4.2 Market Price Trends

```{r market-prices}
prices %>%
  ggplot(aes(x = date, y = price, colour = item)) +
  geom_line(linewidth = 1) +
  geom_point(size = 1.5, alpha = 0.6) +
  facet_wrap(~item, scales = "free_y", ncol = 2) +
  scale_colour_brewer(palette = "Set1") +
  labs(
    title = "Market Input Price Trends — Full Season",
    x = "Date", y = "Price (CAD)"
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "none")
```

---

# 5. Generate CSVs for Tableau Dashboards

## 5.1 greenleaf_master_flat.csv

```{r build-master-flat}
master_flat <- sensor %>%
  left_join(
    plots %>% select(plot_id, treatment, treatment_block,
                     plot_area_m2, plant_density_plants_m2, row_orientation),
    by = "plot_id"
  ) %>%
  left_join(
    greenhouses %>% select(greenhouse_id, structure_type, heating_system,
                           irrigation_system, sensor_density_per_100m2),
    by = "greenhouse_id"
  ) %>%
  left_join(
    farms %>% select(farm_id, farm_name, region,
                     climate_zone, production_system),
    by = "farm_id"
  ) %>%
  left_join(
    costs %>% select(date, plot_id, daily_energy_cost, daily_fertilizer_cost,
                     daily_labor_cost, daily_pesticide_cost, daily_water_cost,
                     daily_total_input_cost, daily_precision_cost,
                     daily_precision_actions_count, daily_total_actions_count,
                     daily_routine_cost),
    by = c("date","plot_id")
  ) %>%
  left_join(
    season %>% select(plot_id, season_yield_kg_m2, marketable_ratio,
                      season_revenue_cad, total_cost_cad, season_profit_cad,
                      season_roi, precision_benefit_cad),
    by = "plot_id"
  ) %>%
  mutate(
    high_stress_flag     = as.integer(plant_stress_index > 0.6),
    critical_stress_flag = as.integer(plant_stress_index > 0.7),
    action_delay_bucket  = case_when(
      action_delay_days == 0 ~ "Same day",
      action_delay_days == 1 ~ "1 day",
      action_delay_days == 2 ~ "2 days",
      TRUE ~ "No action"
    ),
    stress_outcome = case_when(
      post_action_stress_delta_3d < 0 ~ "Improved",
      post_action_stress_delta_3d > 0 ~ "Worsened",
      TRUE ~ "No change"
    ),
    alert_type_clean         = replace_na(alert_type, "No Alert"),
    recommended_action_clean = replace_na(recommended_action, "No Recommendation")
  )

cat("Master flat:", nrow(master_flat), "rows x",
    ncol(master_flat), "columns\n")

write_csv(master_flat, "greenleaf_master_flat.csv")
cat("Saved: greenleaf_master_flat.csv\n")
```

## 5.2 branch2_plot_weekly_scores.csv

```{r build-branch2-scores}
# Most common recommended action per plot per week
recommended <- sensor %>%
  filter(alert_flag == 1, !is.na(recommended_action)) %>%
  group_by(week_num, plot_id) %>%
  summarise(
    top_recommended_action = names(sort(table(recommended_action),
                                        decreasing = TRUE))[1],
    dominant_alert_type    = names(sort(table(alert_type),
                                        decreasing = TRUE))[1],
    .groups = "drop"
  )

branch2 <- sensor %>%
  group_by(week_num, plot_id) %>%
  summarise(
    alert_count      = sum(alert_flag),
    days_observed    = n(),
    action_count     = sum(action_taken, na.rm = TRUE),
    avg_delay        = mean(action_delay_days, na.rm = TRUE),
    max_delay        = max(action_delay_days, na.rm = TRUE),
    avg_stress       = mean(plant_stress_index),
    max_stress       = max(plant_stress_index),
    avg_delta        = mean(post_action_stress_delta_3d, na.rm = TRUE),
    same_day_actions = sum(action_delay_days == 0, na.rm = TRUE),
    delayed_actions  = sum(action_delay_days > 0, na.rm = TRUE),
    crop             = first(crop),
    .groups = "drop"
  ) %>%
  mutate(
    alert_rate   = alert_count / days_observed,
    action_rate  = ifelse(alert_count > 0,
                          action_count / alert_count, 0),
    response_gap = 1 - action_rate,
    delay_score  = avg_delay / 2,
    urgency_score = 0.40 * max_stress +
                    0.25 * alert_rate +
                    0.20 * response_gap +
                    0.15 * delay_score,
    urgency_100  = round(urgency_score / max(urgency_score) * 100, 1)
  ) %>%
  group_by(week_num) %>%
  mutate(rank = rank(desc(urgency_100), ties.method = "dense")) %>%
  ungroup() %>%
  left_join(
    plots %>% select(plot_id, treatment, treatment_block,
                     greenhouse_id, farm_id),
    by = "plot_id"
  ) %>%
  left_join(
    season %>% select(plot_id, season_roi, precision_benefit_cad,
                      season_profit_cad, season_yield_kg_m2, marketable_ratio),
    by = "plot_id"
  ) %>%
  mutate(
    verdict = case_when(
      action_rate < 0.40 & max_stress > 0.70 ~ "Go Now",
      avg_delta > 0 & action_count > 0        ~ "Act + Review",
      action_rate >= 0.70 & avg_delta < 0     ~ "Acting & Working",
      urgency_100 >= 90                        ~ "High Priority",
      TRUE                                     ~ "Monitor"
    ),
    verdict_sort = case_when(
      verdict == "Go Now"           ~ 1,
      verdict == "High Priority"    ~ 2,
      verdict == "Act + Review"     ~ 3,
      verdict == "Acting & Working" ~ 4,
      TRUE                          ~ 5
    )
  ) %>%
  left_join(recommended, by = c("week_num","plot_id")) %>%
  mutate(
    top_recommended_action = replace_na(top_recommended_action, "No alerts"),
    dominant_alert_type    = replace_na(dominant_alert_type, "No alerts")
  )

cat("Branch2:", nrow(branch2), "rows x", ncol(branch2), "columns\n")
cat("Weeks:", n_distinct(branch2$week_num), "\n")

write_csv(branch2, "branch2_plot_weekly_scores.csv")
cat("Saved: branch2_plot_weekly_scores.csv\n")
```

## 5.3 Validation — Week 14 Top 10

```{r validate-week14}
cat("=== Week 14 Top 10 Plots by Urgency Score ===\n")
branch2 %>%
  filter(week_num == 14) %>%
  arrange(verdict_sort, desc(urgency_100)) %>%
  head(10) %>%
  select(rank, plot_id, crop, treatment, urgency_100,
         max_stress, alert_count, action_rate,
         avg_delay, avg_delta, verdict,
         top_recommended_action) %>%
  print()
```

---

# 6. Key Findings Summary

```{r key-findings}
cat("=== FINDING 1 — Speed of Response ===\n")
print(delay_analysis)

cat("\n=== FINDING 2 — Action Rate vs Season ROI ===\n")
print(roi_by_quartile)

cat("\n=== FINDING 3 — Actions That Did Not Reduce Stress ===\n")
pct_failed <- sensor %>%
  filter(action_taken == 1, !is.na(post_action_stress_delta_3d)) %>%
  summarise(pct_no_improvement =
              round(mean(post_action_stress_delta_3d >= 0) * 100, 1))
cat(pct_failed$pct_no_improvement,
    "% of actions did not reduce stress (Act + Review cases)\n")

cat("\n=== FINDING 4 — Stress by Treatment ===\n")
sensor %>%
  left_join(plots %>% select(plot_id, treatment), by = "plot_id") %>%
  group_by(treatment) %>%
  summarise(avg_stress = round(mean(plant_stress_index), 3),
            .groups = "drop") %>%
  arrange(desc(avg_stress)) %>%
  print()
```

---

# Session Info

```{r session-info}
sessionInfo()
```
